Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-04-20 paper.tex
Added files via upload

However, there is a salient piece missing in the turbulent
reacceleration model. It relies heavily on the assumption of an
abundant, volume-filling population of seed suprathermal electrons;
direct Fermi II acceleration from the thermal pool is precluded by
strong Coulomb losses
\citep{2008ApJ...682..175P,2012ApJ...759..113C}. These seeds are
presumed to be either fossil CR electrons (CRes) accelerated by
diffusive shock acceleration (DSA) during structure formation
\citep{1999ApJ...520..529S}, or secondaries injected by hadronic
interaction of CR protons (CRps) with thermal protons
\citep{brunetti11}. While analytic estimates have been made, there has
been no ab initio demonstration that structure formation can lead to
the required abundance of seed electrons with the correct spatial and
spectral characteristics. This is a non-trivial requirement: Coulomb
cooling in dense cluster cores is severe, and DSA fossil electrons may
not survive. On the other hand, for secondaries to constitute the seed
population, the CRp population required in the best-studied case of
the Coma cluster must have a very broad and flat (or even slightly
inverted) spatial profile \citep{brunetti12}, in contrast with the
thermal plasma whose energy density declines steeply with radius. In
the left panel of Fig.~\ref{fig:Edens} we show that such a
distribution is not predicted by cosmological simulations \cite[see
  also][]{pinzke10,2014MNRAS.439.2662V}. If CRps are predominantly
advected with the cluster plasma, their distribution will be peaked
towards the cluster center and shows a similar characteristics as the
thermal plasma. As a consequence, the distribution of secondary
electrons and the resulting radio synchrotron emission is also peaked
since the hadronic reaction is a two-body scattering process (see
Fig.~Fig.~\ref{fig:Edens}). Hence, the simulated emission falls short
of the observed extended and flat radio profile of the Coma cluster.

@@

To pursue these three possibilities further, we employ cosmological
simulations of CRs in clusters. In tandem with new insights from our
recent work on DSA generated fossil electrons \citep{pinzke13}, we
generate the first quantitative calculation of primary and secondary
seed electrons and compare to observations in the Coma cluster. For
the most part, we adopt parameters that are used in previous work: for
details, see \citep[][ turbulent spectrum]{brunetti07,brunetti11},
\citep[][ injection scale of turbulens]{2015ApJ...800...60M},
\citep[][ energy density of
  turbulence]{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
for CR acceleration in shocks, \citep[][ in particular $K_{\rmn{ep}}$,
  acceleration efficiency]{pinzke13}, and for cosmological
simulations, \citep[][ i.e., shock history, temperature profile,
  density profile, magnetic field profile]{pinzke10}. All these
parameters are uncertain, and could potentially change our
predictions. We leave exploration of parameter space and the
interaction between free parameters to future work.

@@

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|{{dp}\over{dt}}\right|_{\rm C} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
- \bnabla\bcdot \vec{F}_\rmn{stream}
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative (r) and Coulomb (C) losses,
$D_{pp}$ is the momentum space diffusion coefficient, and
$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
electrons in the ICM. The $\bnabla\bcdot \bvel$ terms represent
adiabatic gains and losses and the $\bnabla\bcdot
\vec{F}_\rmn{stream}$ terms represent super-Alfv{\'e}nic CR
streaming. For details about $F_\rmn{stream}$ please see
\citet{wiener13}. During post-processing of our Coma-like cluster
simulation, we solve the Fokker-Planck equation over a redshift
interval from $z=5$ to 0. The simulated cluster undergoes a major
merger over the last 1-2~Gyrs that is thought to inject large
turbulent eddies. Following \citet{brunetti07,brunetti11} \citep[see
  also][]{2004ApJ...614..757Y,2015ApJ...800...60M} we assume that
about one Gyr after core passage the fields have decayed down to the
smallest scales where reacceleration is most efficient ($D_{pp}\sim
k_\rmn{cut}$) and the radio halo turns on shortly after. Note that the
exact decay time of the turbulens is of minor importance, since the
thermal and CR quantities are very similar a few 100 Myrs before and
after $z=0$ where we have chosen to evaluate the simulations. This
delay naturally explains why giant radio halos are only seen in a
fraction of all merging clusters. In all our calculations we assume
that turbulent reacceleration efficiently accelerates particles for
$\tau_\rmn{cl}\sim650$~Myrs (which is roughly the cascade time on which
turbulence is damped) and that during this turbulent phase CR
streaming and spatial diffusion can be neglected. In our \Mstream
model, CR streaming and diffusion are incorporated separately during
kinematically quiescent times that precede the merger. As a result,
flat CRp profiles are produced on relatively short timescales ($\sim
0.1-0.5$ Gyr). This allows us to implicitly solve for CR streaming in
our calculations, where we adopt a toy model that enforce a flat CRp
profile at all quiescent times \citep{wiener13}. We assume that CRs
cannot stream significantly past perpendicular $B$-fields at the
accretion shock, so that the total number of CRs is conserved within
the virial radius during the streaming process. Finally, since
streaming is much more efficient for the CRps, we can ignore this
effect for the CRes.

@@

for $k_0<k<k_\rmn{cut}$. Here we adopt an injection scale of the
turbulence, $k_0= 2\pi/(1~\mbox{Mpc})$, motivated by recent
state-of-art simulations
\citep{2009A&A...504...33V,2011A&A...529A..17V,2015ApJ...800...60M}.

@@

  total turbulent energy is typically $10-30$\% of the thermal energy
  in a cluster which is in agreement with our adopted value of
  $X_\rmn{tu}$.}  $X_\rmn{tu}=0.06$ within the radio halo. In this
work we investigate different spatial models for injected
turbulence. With the above choice of normalization, the turbulent
energy density becomes $\epsilon_\rmn{turb} \propto

@@

\Mprimary. Note that in previous work on the Coma cluster,
$\epsilon_\rmn{turb} \propto \epsilon_\rmn{th}$ was adopted which
roughly corresponds to $\alpha_\rmn{tu}= 1$ \citep{brunetti12} and
together with the different distributions for seed CRes constitute the
main differences compared to our work. Our flatter turbulent profiles
are motivated by fits to cosmological simulations

@@

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
  \caption{The ratio of turbulent-to-thermal energy densities (solid
    lines) and cumulative energies (dotted lines) in our three
    models. The energy densities are parametrized as
    $\epsilon_\rmn{turb} \propto
    \epsilon_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
    normalized such that the total turbulent energy in compressible
    modes $E_\rmn{turb}$ for each scenario makes up about 6\% of the
    total thermal energy $E_\rmn{th}$ inside the radio halo
    ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
    the uncertainty in the cluster turbulence and are motivated by the
    cosmological simulation in
    \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}
  \label{fig:Edens}
\end{figure}

For reference we show in Table~\ref{tab:timescales} both the thermal
quantities and the timescales for CR cooling and (re)acceleration for
three different spatial regions of the RH. Interestingly the
reacceleration timescale $\tau_D$ is very similar between our three
models, where the difference comes from turbulent profile
parameterized with $\alpha_\rmn{tu}$. This implies that even small
differences in the turbulent profile could impact the seed CRs
significantly.

\begin{table}
  \caption{Thermal quantities and timescales for different spatial
    regions in a Coma like cluster.}
\begin{tabular}{l c  c c}
\hline
\hline
& & spatial regions & \\
 & $0.1\,\RH^{(2)}$ & $0.3\,\RH^{(2)}$ & $\RH^{(2)}$   \\
\hline
thermal quantities$^{(1)}$ & & & \\
$\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
$T$ [$10^{8}$ K] & 1.4 & 1.0 & 0.58 \\
\hline
timescales$^{(1)}$ & & & \\
$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.45 & 0.44 & 0.39 \\
$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.50 & 0.47 & 0.34 \\
$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.69 & 0.56 & 0.27 \\
$\tau_\rmn{IC/sync}(P=10^4\,m_ec)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
$\tau_\rmn{pp}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
$\tau_\rmn{coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
\hline
\end{tabular}
\begin{quote}
 Notes: \\ 
 (1) Median quantities from our simulated post-merging cluster g72a.\\
 (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
 (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
 (4) Inverse Compton and synchrotron cooling for electrons.\\
 (5) Catastrophic losses for protons.\\
 (6) Coulomb cooling for electrons (protons factor $m_e/m_p$ smaller).\\

@@

\subsection{Spherically symmetric models}

[Anders, your analytical methodology should go here]

\subsection{Cosmological simulation methodology}

In this
paper we focus on our simulated cluster, g72a, which is a massive
$1.6\times10^{15}\,M_\odot$ cluster that experienced a merger about
1-2 Gyrs ago \citep{2009MNRAS.399..497D}. Since the cluster mass,
density and temperature profiles are all similar to the well studied
Coma cluster \citep{2007MNRAS.378..385P,pinzke10}, we will compare our
calculations to radio and gamma-ray observations of Coma.

We use a simple test-particle model for the CR acceleration and
injection, where each shock inject CRs that trace a power-law in
momentum,
\begin{equation}
  f(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,
\end{equation}
determined by the normalization $C(t)$ and the spectral index
$\alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}{(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}$
that depends on the adiabatic index $\gamma_\rmn{ad} = 5/3$ and the
Mach number of the shock $\mathcal{M}$. It is given by the ratio of
the upstream velocity ($u_2$) and the sound speed ($c_s$). The CR
number density and CR energy density are derived from $n_\rmn{CR} =
\int_{p_\rmn{inj}}^\infty \dd p\, f(p)$ and $\epsilon_\rmn{CR} =
\int_{p_\rmn{inj}}^\infty \dd p\, f(p) \,T(p)$, respectively, where
$T(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
particle with momentum $p$. We adopt a fit to Monte Carlo
simulations of the thermal leakage process that relates the momentum
of injected protons ($p_\rmn{inj}$) to the thermal energy
($p_\rmn{th}$) of the shocked plasma \citep{kang11}:
\begin{eqnarray}
  \label{eq:qinj}
  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,k T_2}{m c^2}}\,, \nonumber \\
  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{u_2}{p_{\rmn th}\,c} \left(1+
  \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
\end{eqnarray}
Here $\eb = B_0/B_{\perp}$, $B_0$ is the amplitude of the downstream
MHD wave turbulence, and $B_{\perp}$ is the magnetic field along the
shock normal. The physical range of $\eb$ is quite uncertain due to
complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
which we will later see corresponds to a conservative maximum energy
acceleration efficiency for protons of $10\%$. To derive the
acceleration efficiency, $\zeta_{\rmn inj}$, we first have to infer the
particle injection efficiency, which is the fraction of downstream
thermal gas particles which experience diffusive shock acceleration
\citep[for details see ][]{pinzke13},
\begin{equation}
  \label{eq:eta}
  \eta_\rmn{CR,lin} =
  \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
  \rmn{e}^{-x_\rmn{inj}^2}.
\end{equation}
The particle injection efficiency is a strong function of
$x_\rmn{inj}$ that depends on both $\mathcal{M}$ and $\eb$. The
energy density of CRs that are injected and accelerated at the shock
(neglecting the CR back reaction on the shock) is given by
\begin{equation}
\label{eq:CR_energy} 
  \Delta\epsilon_\rmn{CR,lin} =
  \eta_\rmn{CR,lin}(\mathcal{M})\,T_\rmn{CR}(\mathcal{M},p_\rmn{inj})\,n_\rmn{th}(T_2),
\end{equation}
and the CR energy injection and acceleration efficiency is:
\begin{equation}
  \zeta_\rmn{lin} =
  \frac{\Delta\epsilon_\rmn{CR,lin}}{\Delta\epsilon_\rmn{diss}},
   \quad\mbox{where}\quad
  \Delta\epsilon_\rmn{diss} = \epsilon_\rmn{th2} - \epsilon_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
\label{eqn:energy_frac}  
\end{equation}
The dissipated energy density in the downstream regime,
$\Delta\epsilon_\rmn{diss}$, is given by the difference of the thermal
energy densities in the pre- and post-shock regimes, corrected for the
adiabatic energy increase due to gas compression.

We limit the acceleration efficiency to $\zeta_{\rmn max}$ by
steepening the spectral index of the injected population
$\alpha_\rmn{inj}$ to $\alpha_\rmn{sub}$ so that $\zeta_{\rmn lin}
\leq \zeta_{\rmn max}$ is always fulfilled. The slope
$\alpha_\rmn{inj}$ impact $\zeta_{\rmn inj}$ via the mean energy per
particle given by $T_\rmn{CR} = \epsilon_\rmn{CR}/n_\rmn{CR}$. This
procedure conserves energy and is motivated by models of non-linear
shock acceleration where a sub-shock with a lower compression ratio
(and hence steeper spectral index) forms
\citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$, we
find that for strong shocks where $\alpha \lesssim 2.3$ the spectral
slope is steepened by a maximum of $\sim 10$ per cent in low
temperature regimes ($kT\sim 0.1$~keV), while the steepening is much
smaller for high temperature regimes ($kT\sim 10$~keV) that are more
relevant for clusters. Since $p_{\rm inj}$ remains fixed, so does the
CR number density $n_\rmn{CR}$. Hence we can solve for the
renormalized normalization constant $C_\rmn{sub}$ using $n_\rmn{CR}$
and Eqn.~\ref{eq:eta}:
\begin{equation}
  \label{eq:Cp_sub}
  C_\rmn{sub}=\eta_\rmn{CR,lin}\,(\alpha_\rmn{sub}-1)\,p_\rmn{inj}^{\alpha_\rmn{sub}-1}\,,
\end{equation}
where the new distribution function is given by $f(p,t)= C_\rmn{sub}
p^{-\alpha_\rmn{sub}}$. We set an upper limit on the ratio of
accelerated proton-to-dissipated energy in the downstream of strong
shocks that varies from $\zeta_{\rmn max} \sim 1-10\%$, depending on
the adopted model (for more details, see Section \ref{sec:results}).

>>>>

However, there is a salient piece missing in the turbulent
reacceleration model. It relies heavily on the assumption of an
abundant, volume-filling population of seed suprathermal electrons;
direct Fermi II acceleration from the thermal pool is precluded by
strong Coulomb losses
\citep{2008ApJ...682..175P,2012ApJ...759..113C}. These seeds are
presumed to be either fossil CR electrons (CRes) accelerated by
diffusive shock acceleration (DSA) during structure formation
\citep{1999ApJ...520..529S}, or secondaries injected by hadronic
interaction of CR protons (CRps) with thermal protons
\citep{brunetti11}. While analytic estimates have been made, there has
been no ab initio demonstration that structure formation can lead to
the required abundance of seed electrons with the correct spatial and
spectral characteristics. This is a non-trivial requirement: Coulomb
cooling in dense cluster cores is severe, and DSA fossil electrons may
not survive. On the other hand, for secondaries to constitute the seed
population, the CRp population required in the best-studied case of
the Coma cluster must have a very broad and flat (or even slightly
inverted) spatial profile \citep{brunetti12}, in contrast with the
thermal plasma whose energy density declines steeply with radius. In
Fig.~\ref{fig:Edens} we show that such a distribution is not predicted
by cosmological simulations \cite[see
  also][]{pinzke10,2014MNRAS.439.2662V}. If CRps are predominantly
advected with the cluster plasma, their distribution will be peaked
towards the cluster center and shows a similar characteristics as the
thermal plasma. As a consequence, the distribution of secondary
electrons and the resulting radio synchrotron emission is also peaked
since the hadronic reaction is a two-body scattering process (see
Fig.~\ref{fig:Edens}). Hence, the simulated emission falls short
of the observed extended and flat radio profile of the Coma cluster.

@@

To pursue these three possibilities further, we employ cosmological
simulations of CRs in clusters. In tandem with new insights from our
recent work on DSA generated fossil electrons \citep{pinzke13}, we
generate the first quantitative calculation of primary and secondary
seed electrons and compare to observations in the Coma cluster. For
the most part, we adopt parameters that are used in previous work: for
details, see \citep[][ turbulent spectrum]{brunetti07,brunetti11},
\citep[][ injection scale of turbulens]{2015ApJ...800...60M},
\citep[][ energy density of
  turbulence]{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
for CR acceleration in shocks, \citep[][ in particular $K_{\rmn{ep}}$,
  acceleration efficiency]{pinzke13}, and for cosmological
simulations, \citep[][ i.e., shock history, temperature profile,
  density profile, magnetic field profile]{pinzke10}. All these
parameters are uncertain, and could potentially change our
predictions. We refere the reader to section~\ref{sect:param_comp} for
a small exploration of parameter space, however we leave the full
exploration of parameter space and the interaction between free
parameters to future work.

@@

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|{{dp}\over{dt}}\right|_{\rm coul} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
- \bnabla\bcdot \vec{F}_\rmn{stream}
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative (r) and Coulomb (coul) losses,
$D_{pp}$ is the momentum space diffusion coefficient, and
$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
electrons in the ICM. The $\bnabla\bcdot \bvel$ terms represent
adiabatic gains and losses and the $\bnabla\bcdot
\vec{F}_\rmn{stream}$ terms represent super-Alfv{\'e}nic CR
streaming. For details about $F_\rmn{stream}$ please see
\citet{wiener13}. During post-processing of our Coma-like cluster
simulation, we solve the Fokker-Planck equation over a redshift
interval from $z=5$ to 0. The simulated cluster undergoes a major
merger over the last 1-2~Gyrs that is thought to inject large
turbulent eddies. Following \citet{brunetti07,brunetti11} \citep[see
  also][]{2004ApJ...614..757Y,2015ApJ...800...60M} we assume that
about one Gyr after core passage the fields have decayed down to the
smallest scales where reacceleration is most efficient ($D_{pp}\sim
k_\rmn{cut}$) and the radio halo turns on shortly after. Note that the
exact decay time of the turbulens is of minor importance, since the
thermal and CR quantities are very similar a few 100 Myrs before and
after $z=0$ where we have chosen to evaluate the simulations. This
delay naturally explains why giant radio halos are only seen in a
fraction of all merging clusters. In all our calculations we assume
that turbulent reacceleration efficiently accelerates particles for
$\tau_\rmn{cl}\sim650$~Myrs (which is roughly the cascade time on which
turbulence is damped) and that during this turbulent phase CR
streaming and spatial diffusion can be neglected. In our \Mstream
model, CR streaming and diffusion are incorporated separately during
kinematically quiescent times that precede the merger. As a result,
flat CRp profiles are produced on relatively short timescales ($\sim
0.1-0.5$ Gyr). This allows us to implicitly solve for CR streaming in
our calculations, where we adopt a toy model that enforce a flat CRp
profile at all quiescent times \citep{wiener13}. We assume that CRs
cannot stream significantly past perpendicular $B$-fields at the
accretion shock, so that the total number of CRs is conserved within
the virial radius during the streaming process. Finally, since
streaming is much more efficient for the CRps, we can ignore this
effect for the CRes.

@@

for $k_0<k<k_\rmn{cut}$. Here we adopt a injection scale of the
turbulence, $k_0= 2\pi/(100~\mbox{kpc})$, that is in line with
previous work \citep{brunetti07,brunetti11} \AP{need to be motivated
  beter? why not 1 Mpc}
%, motivated by recent state-of-art simulations \citep{2009A&A...504...33V,2011A&A...529A..17V,2015ApJ...800...60M}.

@@

  total turbulent energy is typically $\sim15-70$\% of the thermal
  energy in a cluster \cite{2011A&A...529A..17V} which is in agreement
  with our adopted value of $X_\rmn{tu}$.}  $X_\rmn{tu}=0.2$ within
the radio halo. In this work we investigate different spatial models
for injected turbulence. With the above choice of normalization, the
turbulent energy density becomes $\epsilon_\rmn{turb} \propto

@@

\Mprimary (see Figure~\ref{fig:turb} for visualisation). Note that in
previous work on the Coma cluster, $\epsilon_\rmn{turb} \propto
\epsilon_\rmn{th}$ was adopted which roughly corresponds to
$\alpha_\rmn{tu}= 1$ \citep{brunetti12} and together with the
different distributions for seed CRes constitute the main differences
compared to our work. Our flatter turbulent profiles are motivated by
fits to cosmological simulations

@@

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
  \caption{The ratio of turbulent-to-thermal energy densities (solid
    lines) and cumulative energies (dotted lines) in our three
    models. The energy densities are parametrized as
    $\epsilon_\rmn{turb} \propto
    \epsilon_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
    normalized such that the total turbulent energy in compressible
    modes $E_\rmn{turb}$ for each scenario makes up about 20\% of the
    total thermal energy $E_\rmn{th}$ inside the radio halo
    ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
    the uncertainty in the cluster turbulence and are motivated by the
    cosmological simulation in
    \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}
  \label{fig:turb}
\end{figure}

For reference we show in Table~\ref{tab:timescales} both the thermal
quantities and the timescales for CR cooling and (re)acceleration for
three different spatial regions of the RH. Interestingly the
reacceleration timescale $\tau_D$ is similar between our three models,
where the difference comes from turbulent profile parameterized with
$\alpha_\rmn{tu}$. This implies that even small differences in the
turbulent profile could impact the seed CRs significantly.

\begin{table}
  \caption{Thermal quantities and timescales for different spatial
    regions in a Coma like cluster.}
\begin{tabular}{l c  c c}
\hline
\hline
& & spatial regions & \\
 & $0.1\,\RH^{(2)}$ & $0.3\,\RH^{(2)}$ & $\RH^{(2)}$   \\
\hline
thermal quantities$^{(1)}$ & & & \\
$\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
$T$ [$10^{8}$ K] & 1.4 & 1.0 & 0.58 \\
\hline
timescales$^{(1)}$ & & & \\
$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.45 & 0.44 & 0.39 \\
$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.50 & 0.47 & 0.34 \\
$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.69 & 0.56 & 0.27 \\
$\tau_\rmn{IC/sync}(P=10^4\,m_ec)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
$\tau_\rmn{had}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
$\tau_\rmn{coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
\hline
\end{tabular}
\begin{quote}
 Notes: \\ 
 (1) Median quantities from our simulated post-merging cluster g72a.\\
 (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
 (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
 (4) Inverse Compton and synchrotron cooling for electrons.\\
 (5) Catastrophic losses for protons.\\
 (6) Coulomb cooling for electrons (protons factor $m_e/m_p$ smaller).\\

@@

\subsection{Spherically symmetric models}
In this section we develope a simple framework that will be used to
test the robustness of our models to the critical parameters for CRs
and turbulence in section~\ref{sect:param_comp}. Here we do not follow
single Lagrangian particles in the cluster, instead we use a more
simple approach where we solve the Fokker-Plack equation in static
spherical shells for injection, reacceleration, and losses of the
CRs. Once the CRs have been reaccelerated for $\tau_\rmn{cl} =
650\,\rmn{Myr}$, we calculate the radio emission and compare the
profile and spectra for different parametrizations.

We adopt both the density \cite{1992A&A...259L..31B} and temperature
\cite{2009ApJ...696.1886B,2001A&A...365L..67A} profiles derived from
X-ray observations of the Coma cluster. They are given by:
\begin{eqnarray}
n_e &=& \frac{3.4\times10^{-3}}{\left[1+\left(R/294\,\rmn{kpc}\right)^2\right]^{1.125}}\nonumber\\
T k_B &=& 8.25\,\rmn{keV} \left[1+\left(R/0.5R_{200}\right)^2\right]^{-0.32}\,.
\end{eqnarray}
The virial radius of Coma is given by $R_{200} = 2300\,\rmn{kpc}$.
The bulk of the CRps are injected by relatively low Mach number shocks
and parametrized by $f_\rmn{CRp,inj}(p) =
C_\rmn{CRp,inj}\,p^{-2.5}$. The CRps trace the thermal gas with
$C_\rmn{CRp,inj} \propto \epsilon_\rmn{th}^{\alpha_\rmn{CR,spat}}$,
where the normalization is fixed by assuming that the injected CR
energy in the last 650~Myrs make up 0.03\% of the thermal energy
inside the virial radius, i.e.
$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj} \rmn{d}
V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V = 0.0003$. The spectrum of
  the initial CRp distibtion is determined by the steady state between
  injection and cooling,
\begin{equation}
 f_{CRp,0} \approx \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
\rmn{d}p'}{\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where the normalization is fixed by
$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj}
\rmn{d}V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V =
0.003$. Similarly, the initial CRe distribution is given by the steady
state between cooling (Coulomb, invers Compton, and synchroton) and
injection of secondary CRes from $f_{CRp,0}$. We also include the
contineous injection of secondary CRes during $\tau_\rmn{cl}$. The
compressible turbulence responsible for reacceleating both the CRps
and CRes is parametrized by $I_0 \propto X_\rmn{tu} (n_e
T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_\rmn{pp}$ is
calculated for each radial bin using
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
are similar to what is used for our simulated cluster.

\subsection{Cosmological simulation methodology}
In this paper we focus on our simulated cluster, g72a, which is a
massive $1.6\times10^{15}\,M_\odot$ cluster that experienced a merger
about 1-2 Gyrs ago \citep{2009MNRAS.399..497D}. Since the cluster
mass, density and temperature profiles are all similar to the well
studied Coma cluster \citep{2007MNRAS.378..385P,pinzke10}, we will
compare our calculations to radio and gamma-ray observations of Coma.
